Assignment 5

### 2015-02-27 rmtw/a5/latex8.tex
adsa
Pushing my bits

\item Selection of primary studies (6.2)
\item Study quality assessment (6.3) x
\item Data extraction and monitoring (6.4) x
\item Data synthesis x
\end{itemize}

>>>>

Trial Search, Checking vs already performed studies.
We picked 6 well known studies, our search strings did manage to find them all.

Didn't check other disciplines as the area is not relevant.

Summarise publication bias.

Table, showing what sources we searched, what dates, what strategy, Years covered by search, what journal and conference proceedings were covered.

Justify the when, the where and the how.

\item Selection of primary studies (6.2)
Sources that provide direct evidence about the research question. Refined search criteria here?

\item Study quality assessment (6.3) x

Apply the inclusion and exclusion criteria here, keeping a list of all excluded articles.

Studies not related to Software Engineering were excluded first and as such have not been included in the exclusion list due to their irrelevance.

Cohen Kappa statistic. Initial value here. Disagreements will be discussed and resolved.

\item Data extraction and monitoring (6.4) x

Quality of the papers must also be considered before they are examined for use in the study, this is done along with the inclusion and exclusion criteria.

\item Data synthesis x
\end{itemize}
